What We Eval in the Shadows

### 2021-04-14 paper/main.tex
Changes

The R language was intended to be extensible. The combination of lazy
evaluation, \c{substitute} and \c{eval} are the tools given to
developers to this end. This API is slightly more complex than just
passing a string, it is conceivable that this may discourage some
casual users. \Eval is also being used to reduce boilerplate code and
provide convenience features for programmers. We now give some
representative examples of its usage.

\mypara{Variable lookup.} % predominant usage of eval in base

>>>>

The R language was intended to be extensible. The combination of lazy
evaluation, \c{substitute} and \c{eval} are the tools given to
developers to this end. This API is slightly more complex than just
passing a string, it is conceivable that this may discourage some
casual users. \Eval is also being used to reduce boilerplate code and
provide convenience features for programmers. We give examples for the minimized expressions of Section~\ref{sec:minimized} and then dig into high-level \eval design patterns.

\mypara{Variable lookup and values.} 
This corresponds to minimized expressions \c{X}, \c{V}. We also include here lookup to slots in a list or data frame, \ie minimized expression \c{\$}.
It is the predominant usage of \eval in Base, through function \c{match.args}. In CRAN, it correlates with more exotic environments passed to \eval.
